---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mtrailz4r

<!-- badges: start -->
[![R-CMD-check](https://github.com/TeroJii/mtrailz4r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/TeroJii/mtrailz4r/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/TeroJii/mtrailz4r/branch/main/graph/badge.svg)](https://app.codecov.io/gh/TeroJii/mtrailz4r?branch=main)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub Release](https://img.shields.io/github/v/release/TeroJii/mtrailz4r)
<!-- badges: end -->

The goal of mtrailz4r is to help with specific data processing steps...

## TO-DO

- [ ] Consider adding a function for extracting user_properties


## Installation

You can install the development version of mtrailz4r from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github(repo = "TeroJii/mtrailz4r")
```

Use the release tags to install a specific version. For example to install version 0.0.7:

``` r
# install.packages("remotes")
remotes::install_github(repo = "TeroJii/mtrailz4r@v0.0.7")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mtrailz4r)
## basic example code
mockdata |> 
  mt4r_unnest() |> 
  mt4r_addsessionid() |>
  mt4r_fixtime() |> 
  plot_exertime()
```

